Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-22 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor intro edits

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, prime candidate sources for authentication have more errors than entropy. 
For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}. Physically inclonable functions suffer from similar problems \lnote{ben please fix}

@@

The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source. \bnote{this should be strengthened.  move negative results to there.} \lnote{waiting for response form Adam}

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.

Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols. It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

We then switch to computational security to obtain constructions with additional features. Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy. However, it provides reusability. The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution.
We note that such strong reusability was shown to be impossible in information-theoretically secure fuzzy extractors~\cite[Theorem 11]{Boyen2004}.\lnote{really? I can't parse his theorem clearly enough} This construction, however, requires that the fraction of errors is subconstant.

@@

Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}. Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret. The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$. To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$. Reusability follows from composable obfuscation.

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers). To tolerate errors, these bits come from an error correcting code. And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.

@@

>>>>

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, prime candidate sources for authentication have more errors than entropy. 
For example, the IrisCode~\cite{daugman2004}, which is the state of the art approach to handling what is believed to be the best biometric \cite{prabhakar2003biometric}, produces a source that more errors than entropy~\cite[Section 5]{blanton2009biometric}. Physical unclonable problems with slightly nonuniform outputs suffer from similar problems~\cite{koeberl2014entropy}.

@@

The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source. \bnote{negative results stated in our contributions. keep there?}

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.  Table~\ref{tab:upper bounds} summarizes our constructions.

Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols. %It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

We switch to computational security to obtain constructions with additional features. Boyen showed information-theoretic reusability fuzzy extractors incur entropy loss proportional to the number of corrected error patterns~\cite[Theorem 11]{Boyen2004}.  For sources with more errors than entropy, information-theoretic reusability is impossible~(see \secref{sec:reusable} for discussion).

Our second construction, like the first, also requires that a constant fraction of symbols contribute fresh entropy. It provides reusability against \emph{computational} adversaries. 
The reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution. 
 This construction, however, requires that the fraction of errors is subconstant. \bnote{reasonable?}

@@

Our second construction, which is computationally secure, is based on obfuscated digital lockers~\cite{canetti2008obfuscating}. Digital lockers output a secret value only when given the correct input to ``unlock'' the secret. An obfuscated digital locker does not provide information about the locked value or how to unlock it.  The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$. To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$. We use obfuscation in a way that does not leak partial information; this is crucial to arguing reusability.

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are simpler to construct than digital lockers). To tolerate errors, these bits come from an error correcting code. To ensure an  adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor) from the decoded string.

@@

\section*{Acknowledgements}
The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
